### 2024-02-19 paper_sisc_first_revision/localpsf.tex
add discussion of frog convergence figure

>>>>

In Figure \ref{fig:PSF_tau_convergence} we show the convergence of the proposed PSF method on the blur kernel as a function of the total number of impulse responses and the number of batches. We show convergence for several ellipsoid size parameters $\tau$, ranging from $2.0$--$4.0$. We observe a roughly linear convergence rate until a limit, which depends on $\tau$, is reached. I.e., the relative error decreases as $\text{constant} \times \left(\# \text{impulse responses}\right)^{-1}$ or $\text{constant} \times \# \text{batches}^{-1}$ until the limit is reached, then the error does not decrease any further. Increasing $\tau$ lowers this limit, allowing the method to achieve higher accuracy. Before this limit is reached, the convergence rate is the same for all $\tau$ as a function the number of impulse responses. This means that the convergence is faster for smaller $\tau$ as a function of the number of batches, since smaller $\tau$ means more impulse responses per batch.
